### 2017-01-23 chapters/ch2-bottom-up.tex
Some ideas and questions. Thanks @Zhijieren

\section{Limitations, Discussion and Questions}
\begin{itemize}
\item What's the mechanisms for publishing double-spends?
\item Doesn't prevent spam, so DoS is possible. But we can work around this by
  ignoring spammy nodes.
\item If there is stake in the system, we can use it to elect validator, this
  would prevent the sybil attack. But I argue sybil attack is application
  dependent.
\item No incentive in this system, but again it's application specific.
\item If a node is offline for some time, it will not be in any consensus group.
  To join a consensus group, it must make a transaction to a node that is in a
  consensus group.
\item Not all the validators are online (chrun), but we can model it using the
  Sleep consensus model~\cite{bentov2016sleepy}.
\item This model does not require a single connected component. 
\item I personally don't see a lot of benefit with the idea of spontaneously
  growing the set of valid transaction by traversing the DAG, in the end
  everything must be validated anyway, and I don't see any major advantages of
  that technique. It also must assume single connected component, where as this
  approach does not.
\end{itemize}

@@

\section{Is the traditional Byzantine Agreement too strict?}
If nodes are in agreement, they share the same state machine. But is this too
strict for our use case?

Suppose there is set of transactions $A \rightarrow B \rightarrow C \rightarrow
D$ that depend on each other. Then half of the nodes agree on a subset of those
transactions, i.e. $\{A, B, C\}$. Another half agree on all four transactions.
This is not Byzantine agreement in the traditional sense, because there does not
exist a majority that share the same state machine. But indirectly they all
agree on the set intersection. Can we build a model that support this type of
consensus?

>>>>

\section{Limitations, Discussion and Questions}
\begin{itemize}
\item What's the mechanisms for publishing double-spends?
\item Doesn't prevent spam, so DoS is possible. But we can work around this by
  ignoring spammy nodes.
\item If there is stake in the system, we can use it to elect validator, this
  would prevent the sybil attack. But I argue sybil attack is application
  dependent.
\item No incentive in this system, but again it's application specific.
\item If a node is offline for some time, it will not be in any consensus group.
  To join a consensus group, it must make a transaction to a node that is in a
  consensus group.
\item Not all the validators are online (chrun), but we can model it using the
  Sleep consensus model~\cite{bentov2016sleepy}.
\item This model does not require a single connected component. 
\item I personally don't see a lot of benefit with the idea of spontaneously
  growing the set of valid transaction by traversing the DAG, in the end
  everything must be validated anyway, and I don't see any major advantages of
  that technique. It also must assume single connected component, where as this
  approach does not.
\item What if no or very few transactions happen in a consensus run? How do we
  select validators in this case? Perhaps select validators according to a
  different metric. Closeness metric between the hash and some value perhaps.
\item Given a transaction, how does a node efficiently validate its G
  authenticity?
\item Force nodes to only create checkpoint when their previous checkpointed
  chain has been validated?
\end{itemize}

@@
